251 MA

### 2023-03-06 code/process.Rmd
run rest of pre-reg models

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
library(Replicate)
library(metafor)
library(esc)
library(here)
library(brms)
library(rstan)
library(googledrive)
library(glmnet)

@@

```{r}
library(ggstance)
d_es_predInt |> ggplot(aes(x=target_ES, 
                           xmin=target_ES-target_SE*1.96,
                           xmax=target_ES+target_SE*1.96, 
                           y=rep_ES,
                           ymin=rep_ES-rep_SE*1.96,
                           ymax=rep_ES+rep_SE*1.96,
                           color=p_orig))+
  geom_linerange(alpha=.5)+
  geom_linerangeh(alpha=.5)+
  geom_point()+
  coord_cartesian(xlim=c(-1,12), ylim=c(-1,12))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="p_orig", x="Original ES", y="Replication ES")

@@

@@

```{r}
library(tidybayes)
tier1_subjective |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
```

```{r, eval=F}
tier2_predint <- brm(pred_int ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                       z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                       (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                     family="bernoulli",
                     data=data_tier2,
                     file=here(model_location, "tier2_predint"),
                     prior=priors, 
                     control=list(adapt_delta=.99),
                     backend="cmdstanr")
```

```{r, eval=F}
tier2_porig <- brm(porig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                     z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                     (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                        z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                   data=data_tier2,
                   file=here(model_location, "tier2_porig"),
                   prior=priors, 
                   control=list(adapt_delta=.99),
                   backend="cmdstanr")
```

```{r, eval=F}
tier3_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          z_target_d_calc + z_log_p+ 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                             z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                             z_target_d_calc + z_log_p| academic_year),
                        family="bernoulli",
                        data=data_tier3,
                        file=here(model_location, "tier3_subjective"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```

```{r, eval=F}
tier3_predint <- brm(predint ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                       z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                       z_target_d_calc + z_log_p+ 
                       (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          z_target_d_calc + z_log_p| academic_year),
                     family="bernoulli",
                     data=data_tier3,
                     file=here(model_location, "tier3_predint"),
                     prior=priors, 
                     control=list(adapt_delta=.99),
                     backend="cmdstanr")
```

```{r, eval=F}
tier3_porig <- brm(p_orig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                     z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                     z_target_d_calc + z_log_p+ 
                     (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                        z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                        z_target_d_calc + z_log_p| academic_year),
                   family=(link="logit"),
                   data=data_tier3,
                   file=here(model_location, "tier3_porig"),
                   prior=priors, 
                   control=list(adapt_delta=.99),
                   #backend="cmdstanr"
)
```

@@

```{r}
library("lattice")
dat <- data_tier1 |> mutate(is.cog=ifelse(subfield=="cognitive", 1,0),
                            is.soc=ifelse(subfield=="social", 1,0),
                            is.other=ifelse(subfield=="other-psych", 1,0),
                            is.non=ifelse(subfield=="non-psych",1,0)) |> 
  select(is.cog, is.soc, is.other, is.non,stanford, z_pub_year, open_data, open_mat,  change_platform, 
         z_log_ratio_ss, z_log_sample, single_vignette, z_log_trials, is_within, )

@@

# Install and load reshape2 package
library(reshape2)

@@

# plotting the correlation heatmap
library(ggplot2)
ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
                                   fill=value)) + #scale_fill_viridis()+
  scale_fill_gradient2(low="#440154",high="#FDE725FF")+
  geom_tile(alpha=.7)+theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1))+geom_text(aes(label=value), size=3)+
  labs(x="", y="", fill="Correlation")

@@

```{r}
library(ggrepel)
library(ggthemes)
to_plot <- lasso_linear2$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(`s0`:`s71`) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())

@@

### TODO predictive

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
library(Replicate)
library(metafor)
library(esc)
library(here)
library(brms)
library(rstan)
library(googledrive)
library(glmnet)
library(tidybayes)
library(ggstance)
library("lattice")
library(reshape2)
library(ggrepel)
library(ggthemes)

@@

```{r}
d_es_predInt |> ggplot(aes(x=target_ES, 
                           xmin=target_ES-target_SE*1.96,
                           xmax=target_ES+target_SE*1.96, 
                           y=rep_ES,
                           ymin=rep_ES-rep_SE*1.96,
                           ymax=rep_ES+rep_SE*1.96,
                           color=p_orig))+
  geom_linerange(alpha=.5)+
  geom_linerangeh(alpha=.5)+
  geom_point()+
  coord_cartesian(xlim=c(-1,12), ylim=c(-1,12))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="p_orig", x="Original ES", y="Replication ES")

@@

Note: tier 2 and 3 models are subject to change as a few more studies might in fact have useable stats & some of the effect size extraction might be incorrect.

@@

```{r}
tier1_subjective |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
```

```{r, eval=T}
tier2_predint <- brm(predInt ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                       z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                       (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                     family="bernoulli",
                     data=data_tier2,
                     file=here(model_location, "tier2_predint"),
                     prior=priors, 
                     control=list(adapt_delta=.99),
                     backend="cmdstanr")
```

```{r}
tier2_predint |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
```

```{r, eval=T}
tier2_porig <- brm(p_orig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                     z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                     (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                        z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                   data=data_tier2,
                   file=here(model_location, "tier2_porig"),
                   prior=priors, 
                   control=list(adapt_delta=.99),
                   backend="cmdstanr")
```

```{r}
tier2_porig |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
```
```{r, eval=T}
tier3_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          z_target_d_calc + z_log_p+ 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                             z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                             z_target_d_calc + z_log_p| academic_year),
                        family="cumulative",
                        data=data_tier3 |> mutate(sub_rep=sub_rep*4+1),
                        file=here(model_location, "tier3_subjective"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```

```{r}
tier3_subjective |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
```

```{r, eval=T}
tier3_predint <- brm(predInt ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                       z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                       z_target_d_calc + z_log_p+ 
                       (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          z_target_d_calc + z_log_p| academic_year),
                     family="bernoulli",
                     data=data_tier3,
                     file=here(model_location, "tier3_predint"),
                     prior=priors, 
                     control=list(adapt_delta=.99),
                     backend="cmdstanr")
```

```{r}
tier3_predint |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
```

```{r, eval=F}
tier3_porig <- brm(p_orig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                     z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                     z_target_d_calc + z_log_p+ 
                     (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                        z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                        z_target_d_calc + z_log_p| academic_year),
                   data=data_tier3,
                   file=here(model_location, "tier3_porig"),
                   prior=priors, 
                   control=list(adapt_delta=.99),
                   backend="cmdstanr"
)
```

```{r}
tier3_porig |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
```

## Sensitivity analysis TODO

@@

```{r}
dat <- data_tier1 |> mutate(is.cog=ifelse(subfield=="cognitive", 1,0),
                            is.soc=ifelse(subfield=="social", 1,0),
                            is.other=ifelse(subfield=="other-psych", 1,0),
                            is.non=ifelse(subfield=="non-psych",1,0)) |> 
  select(is.cog, is.soc, is.other, is.non,stanford, z_pub_year, open_data, open_mat,  change_platform, 
         z_log_ratio_ss, z_log_sample, single_vignette, z_log_trials, is_within, )

@@

# Install and load reshape2 package

@@

# plotting the correlation heatmap
ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
                                   fill=value)) + #scale_fill_viridis()+
  scale_fill_gradient2(low="#440154",high="#FDE725FF")+
  geom_tile(alpha=.7)+theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1))+geom_text(aes(label=value), size=3)+
  labs(x="", y="", fill="Correlation")

@@

to_plot <- lasso_linear2$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(`s0`:`s71`) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())

@@

## TODO predictive
